Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-06-29 Journal1/paper5TNSM/pr.tex
Add files

\textcolor{MidnightBlue}{Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously. In view of this, a new RAN paradigm, called open RAN (O-RAN), which is shown in Fig \ref{fig:c11}, is introduced to deal with these issues.}
%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

@@

\textcolor{MidnightBlue}{In this paper, we aim to enhance the resource utilization of a downlink O-RAN system and optimize the baseband resource allocation to develop an isolated network slicing outline for different types of services in an O-RAN platform.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.}

In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
\begin{itemize}
\item \textcolor{MidnightBlue}{We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs association, and VNF activation to maximize the weighted throughput of the O-RAN.}
\item \textcolor{MidnightBlue}{We propose an algorithm for resource management in a two-step, with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
In the first step, we reformulate and simplify the problem to find an upper and lower bound for the number of activated VNFs and use the Lagrangian function and KKT conditions to find optimal power and PRB allocation. For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.}
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\item \textcolor{MidnightBlue}{We perform numerical experiments to analyze the performance of the proposed algorithm, which proves to have a higher data rate than both the baseline scheme and data-driven method. Interestingly, our results show that this algorithm performs close to the optimal solution in low interference.}
\end{itemize}

The rest of this paper is organized as follows.
Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
The system model and the problem formulation are described in Section \ref{systemmodel}. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Finally, Section \ref{conc} concludes the paper.
\begin{table}[H]
 \caption {List of Acronyms} \label{table:1a}
 \begin{center}
 \scalebox{0.8}{
  \begin{tabular}{||c | c ||}
  \hline
Abbreviation & Explanation \\ [0.5ex]
  \hline\hline
  VNF & Virtual Network Function\\
  \hline
  VM & Virtual Machine  \\
  \hline
 O-RAN & Open RAN  \\
  \hline
  RAN &  Radio Access Network \\
  \hline
   QoS &  Quality of service \\
  \hline
  PRB &  Physical Resource Block \\
  \hline
  eMBB & enhanced Mobile BroadBand \\
  \hline
  URLLC  & Ultra-Reliable Low Latency Communication \\
   \hline
  mMTC &  massive Machine-To-Machine Communications \\
  \hline
  O-RU &  O-RAN Radio Unit \\
  \hline
   O-DU &  O-RAN Distributed Unit \\ [.5ex]
  \hline
   O-CU &  O-RAN Central Unit \\ [.5ex]
  \hline
  UPF &  User Plane Function \\ [.5ex]
  \hline
 \end{tabular}}
 \end{center}
 \end{table}
\section{Related Literature}\label{RL}
The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), and the allocation of BBU capacity. Also, the allocation of power and physical resource blocks (PRB) is performed at the lower level.
In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).

@@

\text{subject to} \quad  &  P_r \leq P^{max}_{r} \quad \forall r

@@

& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18-1} \\
& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\

@@

& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c21}

@@

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$.
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{subequations}\label{lb1}
\begin{alignat}{4}
\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
\end{alignat}
\end{subequations}
Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability. We notice that it makes the formulation simpler. However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner. Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and we have
$T^{\text{proc}}_{s} =  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}$. So,
$T^{\text{proc}}_{s}=  T^{RU}_{s} + 3\times T^{DU}_{s}.$
%\begin{equation}
%\begin{split}
%T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
%                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
%\end{split}
%\end{equation}

@@

$ \forall i,\forall s$

@@

&M_s \geq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\

@@

\alpha_s/\mu_s\leq M_s \leq \min\{M^{\max}, \phi_{\max}/{3\phi_s}\}

@@

\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s

@@

For the right side, by reformulating the equation \eqref{eqDelay}, we have a new constraint $\forall i, \forall s$ as below,

@@

\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}\\
& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}

@@

\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\
P_r &\leq  \zeta_{r}.\\

@@

\eta_{u_{(s,i)}}&= \max\{\mathcal{R}_{u_{(s,i)}}^{\min}, \lambda_{u_{(s,i)}}+1/T^s_{\max}, \varpi_{u(s,i)} \}, \\
\mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\

@@

\begin{subequations}\label{lagrang}

@@

The derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{P}$ and $\boldsymbol{E}$ give the Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal value of these two variables \cite{lee2018dynamic,ali2018joint}.

@@

\textit{Greedy Algorithm Assignment (GAA):}
The problem can be reformulated as follow
\begin{subequations}\label{problem2}
\begin{alignat}{4}
\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R} \delta_s g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
\text{subject to} \quad  & \sum_{s=1}^{S}\sum_{i=1}^{U_s} g_{u(s,i)}^r \psi_{r,u(s,i)}\leq \mathfrak{t}_r \quad \forall r
 \label{p11} \\
& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{p12}\\
 & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{p13}
\end{alignat}
\end{subequations}
Where $ \psi_{r,u(s,i)}=\sum_{k=1}^{K_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k}  e^k_{r,u(s,i)}$
and $\mathfrak{t}_r = \zeta_r- \sigma_r$  because of the equations \eqref{pr11} and \eqref{pr}.
Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
%The problem \eqref{problem2} is an integer linear programming.
%By changing inequality \eqref{p12} to equality ($\sum_{r}g^r_{u(s,i)} = 1$),
The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.
We solve this problem using heuristic method(GAA method \ref{alg1}), which is a greedy algorithm \cite{akccay2007greedy,lee2018dynamic}.
Firstly, we set all the variables to zero ($g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$).
Then we define the parameter ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$. This parameter is used as a set of O-RUs that can be assigned to the UE $i$ in slice $s$, which initially includes all the O-RUs (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}, \forall s, \forall i$ ).
Also we introduce another parameter $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
which is the knapsack capacity of each O-RU.
Next, we sort all the slices based on their priority.
Afterward, based on the sorting of the UEs,
we assign the O-RU that provides the highest achievable data rate for each UE on the condition that the value of the desired UE ($\psi_{r,u(s,i)}$) does not exceed the knapsack capacity of each O-RU ($ \mathfrak{C}_r$).
If it exceeds the capacity of the desired O-RU, we remove the specific O-RU from the set of O-RUs that can be assigned to that UE (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = {\mathfrak{B}}^{rem}_{u_{(s,i)}} \setminus \{{r^*}\} $). Then, the O-RU with the highest achievable data rate from the new set of O-RUs ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$ is selected.
The complexity of sorting S slices based on their priority is $O(Slog(S))$.
Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ as the whole number of UEs in the system.
The complexity order of this algorithm is about $O(Slog(S)) + O(R\times \mathfrak{N})$.
%$O(N\times \mathfrak{N})$
\begin{algorithm}
\small
%\setstretch{1.}
\caption{Greedy Algorithm for Assignment of O-RU to UEs (GAA)}\label{alg1}
\begin{algorithmic}[1]
\State Set $g^r_{u(s,i)} = 0$, $\mathfrak{C}_r = \mathfrak{t}_r,$ and ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$   $\forall s, \forall i, \forall r$.\label{31}
\State Sort slices according to their priority factor ($\delta_s$) in descending order
\For {$s \gets 1$ to $S$}\label{33}
\For {$i \gets 1$ to $U_s$}
\State $RU = 0$
\For {$r \gets 1$ to $R$}
\State Acquire $\mathfrak{G}^r_{u_{(s,i)}} = \bar{\mathcal{R}}^r_{u_{(s,i)}}$
\EndFor
\State \textbf{end for}
\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
\While{$RU == 0$}
\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$}
\State Set $g^{r^*}_{u(s,i)} = 1$
\State Set  $\mathfrak{C}_{r^*} = \mathfrak{C}_{r^*} - \psi_{{r^*},u(s,i)}$
\State Set $RU = 1$
\Else
\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = {\mathfrak{B}}^{rem}_{u_{(s,i)}} \setminus \{{r^*}\} $
\EndIf
\State \textbf{end if}
\EndWhile
\State \textbf{end while}
\EndFor
\State \textbf{end for}
\EndFor
\State \textbf{end for} \label{34}
\end{algorithmic}
\end{algorithm}

@@

The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$.

@@

and the complexity order of the second sub-problem is about $O(Slog(S)) + O(R\times \mathfrak{N})$.
So the complexity of the main problem \eqref{problem} is $O(T_{conv} \times \mathfrak{N} \times K \times (Slog(S)+R\mathfrak{N}))$.

>>>>

\textcolor{MidnightBlue}{Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously. In view of this, a new RAN paradigm, called open RAN (O-RAN), which is shown in figure \ref{fig:c11}, is introduced to deal with these issues.}
%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

@@

\textcolor{MidnightBlue}{In this paper, we aim to enhance the resource utilization of a downlink O-RAN system and optimize the baseband resource allocation to develop an isolated network slicing outline for the three 5G service classes.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
 The main contributions of this paper are summarized as follows:
\begin{itemize}
\item \textcolor{MidnightBlue}{We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs association, and VNF activation to maximize the weighted throughput of the O-RAN.}
\item \textcolor{MidnightBlue}{We propose a two-step resource management algorithm for solving the optimization problem.
In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs. Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation. In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.}
\item \textcolor{MidnightBlue}{We provide insights into the complexity of our algorithms. Moreover, we analyze and guarantee the convergence of the algorithms. Additionally, we demonstrate the feasibility region of our system using a fast algorithm.}
\item \textcolor{MidnightBlue}{We show via numerical results that the proposed algorithm outperforms two baseline schemes, i.e., the DR scheme and the baseline scheme, in terms of achievable data rate. Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.}
\end{itemize}

The rest of this paper is organized as follows.
Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
The system model and the problem formulation are described in Section \ref{systemmodel}. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Finally, Section \ref{conc} concludes the paper.
\begin{table}[H]
 \caption {List of Acronyms} \label{table:1a}
 \begin{center}
 \scalebox{0.8}{
  \begin{tabular}{||c | c ||}
  \hline
Abbreviation & Explanation \\ [0.5ex]
  \hline\hline
  VNF & Virtual Network Function\\
  \hline
  VM & Virtual Machine  \\
  \hline
 O-RAN & Open RAN  \\
  \hline
  RAN &  Radio Access Network \\
  \hline
   QoS &  Quality of service \\
  \hline
  PRB &  Physical Resource Block \\
  \hline
  eMBB & enhanced Mobile BroadBand \\
  \hline
  URLLC  & Ultra-Reliable Low Latency Communication \\
   \hline
  mMTC &  massive Machine-To-Machine Communications \\
  \hline
  O-RU &  O-RAN Radio Unit \\
  \hline
   O-DU &  O-RAN Distributed Unit \\ [.5ex]
  \hline
   O-CU &  O-RAN Central Unit \\ [.5ex]
   \hline
     UPF &  User Plane Function \\ [.5ex]
  \hline
  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
  \hline
 \end{tabular}}
 \end{center}
 \end{table}
\section{Related Literature}\label{RL}
The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), and the allocation of BBU capacity. Also, the allocation of power and physical resource blocks (PRB) is performed at the lower level.
In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).

@@

\text{subject to} \quad  &  P_r \leq P^{max}_{r} \quad \forall r,

@@

& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r, \label{c18-1} \\
& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r, \label{c18} \\

@@

& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i. \label{c21}

@@

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$.
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{subequations}\label{lb1}
\begin{alignat}{4}
\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\
 \hat{\zeta}_{u(s_j,i)}^{k} =& \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
\end{alignat}
\end{subequations}
Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability. We notice that it makes the formulation simpler. However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner. Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and we have
$T^{\text{proc}}_{s} =  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}$. So,
$T^{\text{proc}}_{s}=  T^{RU}_{s} + 3\times T^{DU}_{s}.$
%\begin{equation}
%\begin{split}
%T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
%                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
%\end{split}
%\end{equation}

@@

%$ \forall i,\forall s$

@@

&M_s \geq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }

@@

\alpha_s/\mu_s\leq M_s \leq \min\{M^{\max}, \phi_{\max}/{3\phi_s}\}.

@@

\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s.

@@

For the right side, by reformulating the equation \eqref{eqDelay}, we have a new constraint $\forall i, \forall s$ given by

@@

\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}, \\
\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s},\\
& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}.

@@

P_r\leq \zeta_r= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}. 

@@

\mathcal{\bar{R}}_{u_{(s,i)}} \geq\eta_{u_{(s,i)}}= \max\{\mathcal{R}_{u_{(s,i)}}^{\min}, \lambda_{u_{(s,i)}}+1/T^s_{\max}, \varpi_{u(s,i)} \}. 

@@

\begin{equation}\label{lagrang}

@@

The derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{P}$ and $\boldsymbol{E}$ give the KKT conditions to obtain the optimal value of these two variables \cite{lee2018dynamic,ali2018joint}.

@@

\textit{Greedy Algorithm Assignment (GAA):}
The problem can be reformulated as follow
\begin{subequations}\label{problem2}
\begin{alignat}{4}
\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R} \delta_s g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
\text{subject to} \quad  & \sum_{s=1}^{S}\sum_{i=1}^{U_s} g_{u(s,i)}^r \psi_{r,u(s,i)}\leq \mathfrak{t}_r \quad \forall r,
 \label{p11} \\
& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{p12}\\
 & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{p13}
\end{alignat}
\end{subequations}
where $ \psi_{r,u(s,i)}=\sum_{k=1}^{K_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k}  e^k_{r,u(s,i)}$
and $\mathfrak{t}_r = \zeta_r- \sigma_r$  because of the equations \eqref{pr11} and \eqref{pr}.
Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
%The problem \eqref{problem2} is an integer linear programming.
%By changing inequality \eqref{p12} to equality ($\sum_{r}g^r_{u(s,i)} = 1$),
The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.
We solve this problem using heuristic method(GAA method \ref{alg1}), which is a greedy algorithm \cite{akccay2007greedy,lee2018dynamic}.
Firstly, we set all the variables to zero ($g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$).
Then we define the parameter ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$. This parameter is used as a set of O-RUs that can be assigned to the UE $i$ in slice $s$, which initially includes all the O-RUs (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}, \forall s, \forall i$ ).
Also we introduce another parameter $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
which is the knapsack capacity of each O-RU.
Next, we sort all the slices based on their priority.
Afterward, based on the sorting of the UEs,
we assign the O-RU that provides the highest achievable data rate for each UE on the condition that the value of the desired UE ($\psi_{r,u(s,i)}$) does not exceed the knapsack capacity of each O-RU ($ \mathfrak{C}_r$).
If it exceeds the capacity of the desired O-RU, we remove the specific O-RU from the set of O-RUs that can be assigned to that UE (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = {\mathfrak{B}}^{rem}_{u_{(s,i)}} \setminus \{{r^*}\} $). Then, the O-RU with the highest achievable data rate from the new set of O-RUs ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$ is selected.
The complexity of sorting S slices based on their priority is $O(Slog(S))$.
Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ as the whole number of UEs in the system.
The complexity order of this algorithm is about $O(Slog(S)) + O(R\times \mathfrak{N})$.
%$O(N\times \mathfrak{N})$
\begin{algorithm}
\small
%\setstretch{1.}
\caption{Greedy Algorithm for Assignment of O-RU to UEs (GAA)}\label{alg1}
\begin{algorithmic}[1]
\State Set $g^r_{u(s,i)} = 0$, $\mathfrak{C}_r = \mathfrak{t}_r,$ and ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$   $\forall s, \forall i, \forall r$.\label{31}
\State Sort slices according to their priority factor ($\delta_s$) in descending order
\For {$s \gets 1$ to $S$}\label{33}
\For {$i \gets 1$ to $U_s$}
\State $RU = 0$
\For {$r \gets 1$ to $R$}
\State Acquire $\mathfrak{G}^r_{u_{(s,i)}} = \bar{\mathcal{R}}^r_{u_{(s,i)}}$
\EndFor
\State \textbf{end for}
\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
\While{$RU == 0$}
\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$}
\State Set $g^{r^*}_{u(s,i)} = 1$
\State Set  $\mathfrak{C}_{r^*} = \mathfrak{C}_{r^*} - \psi_{{r^*},u(s,i)}$
\State Set $RU = 1$
\Else
\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = {\mathfrak{B}}^{rem}_{u_{(s,i)}} \setminus \{{r^*}\} $
\EndIf
\State \textbf{end if}
\EndWhile
\State \textbf{end while}
\EndFor
\State \textbf{end for}
\EndFor
\State \textbf{end for} \label{34}
\end{algorithmic}
\end{algorithm}

@@

The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}U_S$.

@@

and the complexity order of the second sub-problem is about $O(S\log(S)) + O(R\times \mathfrak{N})$.
So the complexity of the main problem \eqref{problem} is $O(T_{conv} \times \mathfrak{N} \times K \times (S\log(S)+R\mathfrak{N}))$.
